A publishing infrastructure for AI-assisted academic authoring

### 2024-03-25 latex/manuscript.tex
latex: update code/data statement

The manuscripts' text used for evaluation in this article are available on their GitHub repositories, at \url{https://github.com/greenelab/ccc-manuscript}, \url{https://github.com/greenelab/phenoplier_manuscript} and \url{https://github.com/greenelab/manubot-gpt-manuscript}.
The source code of the Manubot AI Editor is available on GitHub, at \url{https://github.com/manubot/manubot-ai-editor}.

>>>>

The manuscripts' text and PRs used for human assessment are available on their GitHub repositories, at \url{https://github.com/greenelab/ccc-manuscript}, \url{https://github.com/greenelab/phenoplier_manuscript} and \url{https://github.com/greenelab/manubot-gpt-manuscript}.
The manuscripts' text and PRs used for the automated assessment are available at \url{https://github.com/pivlab/manubot-ai-editor-code-test-mutator-epistasis-manuscript}, \url{https://github.com/pivlab/manubot-ai-editor-code-test-biochatter-manuscript}, \url{https://github.com/pivlab/manubot-ai-editor-code-test-phenoplier-manuscript}, and \url{https://github.com/pivlab/manubot-ai-editor-code-test-ccc-manuscript}.
The source code of the Manubot AI Editor is available at \url{https://github.com/manubot/manubot-ai-editor} and the code for the automated assessment of paragraph quality is available at \url{https://github.com/pivlab/manubot-ai-editor-code}.
